Analysis of Climate Sensitivity using HadAM3

### 2014-04-27 article.tex
Add captions to figures, crop figures.

\begin{figure}[hbp]
    \centering
    \includegraphics[width=\textwidth]{figures/global_temp_precip}
    \caption{Caption.}
    \label{fig:global_temp_precip}
\end{figure}

@@

\begin{figure}[hbp]
    \centering
    \includegraphics[width=\textwidth]{figures/sa_seasonal}
    \caption{Caption.}
    \label{fig:sa_seasonal}
\end{figure}

@@

\begin{figure}[hbp]
    \centering
    \includegraphics[width=\textwidth]{figures/sa_diff}
    \caption{Caption.}
    \label{fig:sa_diff}
\end{figure}

@@

Paragraph about Figure \ref{fig:corr} plots.
\begin{figure}[hbp]
    \centering
    \includegraphics[width=\textwidth]{figures/corr}
    \caption{Caption.}
    \label{fig:corr}
\end{figure}

>>>>

\begin{figure}[hbp]
    \centering
    \includegraphics[width=\textwidth]{figures/global_temp_precip}
    \caption{Global annual, December-February (DJF) and June-August (JJA) maps of the difference between the 1\%py and control scenarios for surface temperature and precipitation (top three left and right). Seasonal and zonal mean differences between the 1\% and control scenarios for temperature and precipitation (bottom two left and right).}
    \label{fig:global_temp_precip}
\end{figure}

@@

\begin{figure}[hbp]
    \centering
    \includegraphics[width=\textwidth]{figures/sa_seasonal}
    \caption{Seasonal variation of the difference between the 1\%py and control scenarios for precipitation and surface temperature for South America.}
    \label{fig:sa_seasonal}
\end{figure}

@@

\begin{figure}[hbp]
    \centering
    \includegraphics[width=\textwidth]{figures/sa_diff}
    \caption{Annual mean of the difference between the 1\%py and control scenarios for precipitation, surface temperature, humidity, NPP, and soil moisture for South America.}
    \label{fig:sa_diff}
\end{figure}

@@

Paragraph about Figure \ref{fig:corr} plots.
\begin{figure}[hbp]
    \centering
    \includegraphics[width=\textwidth]{figures/corr}
    \caption{Scatter plots of the difference between the 1\%py and control scenarios for precipitation, surface temperature, humidity, NPP, and soil moisture for South America. Each pair of variables is represented once. Pearson's r value is shown. For all graphs apart from humidity-surface temperature $p < 0.001$, for humidity-surface temperature $p = 0.034$. }
    \label{fig:corr}
\end{figure}
